When are Fuzzy Extractors Possible?

### 2014-10-06 info-bounds/FuzzyExtPossibility.tex
capitalize section headings

\paragraph{Fuzzy Min-entropy}
We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$, thus subverting the security of $\key$ by running $\rep$. Suppose $w$ is sampled from a distribution $W$.   To have the maximum chance that $w'$ is within distance $t$ of $w$, the adversary would want to maximize the total probability mass of $W$ within the ball $B_t(w')$ of radius $t$ around $w'$.
We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_{w'} \Pr[W\in B_t(w')]$.  Observe that this quantity can be bounded in terms of min-entropy: $\Hoo(W) \ge \Hfuzz(W) \ge \Hoo(W)-\log |B_t|$.

@@

In the fuzzy extractor case, the nonsecret value $p$ partitions the metric space into regions that produce a consistent value under $\rep$ (preimages of each $\key$ under $\rep(\cdot, p)$).  For each of these regions, the adversary knows that possible $w$ lie $t$-far from the boundary of the region.  However, in the Hamming space, the vast majority of points lie near the boundary (this follows by combining the isoperimetric inequality~\cite{harper1966optimal} showing that the ball has the smallest boundary and Hoeffding's inequality~\cite{hoeffding1963probability} for bounding the volume that is $t$-away from this boundary).  This allows the adversary to rule out so many possible $w$ that, combined with the adversarial knowledge of the affine line, most regions become empty, leaving $\key$ far from uniform.

The result for fuzzy extractors is delicate.  The fact that $p$ partitions the space~(into non overlapping regions) relies on perfect correctness.  Extending this result to imperfect correctness seems challenging and is an interesting open problem.
The result also relies on the majority of points lying near boundaries of a set. Indeed, fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set is not the majority of its area.\bnote{cite cite cite!!!}

\subsection{Sufficiency of $\Hfuzz(W)$ in related settings}
\label{sec:related settings}
\bnote{this needs work}
We have evidence that fuzzy min-entropy is sufficient in settings related to information-theoretic fuzzy extractors.  
%We first consider the interactive setting.  
First, an alternate definition fuzzy extractors and secure sketches may provide computational security instead of information-theoretical security~\cite{fuller2013computational}.  In this setting, under the strong assumption of semantically-secure multilinear maps, fuzzy extractors and secure sketches can be constructed for any distribution $W$~\cite{BitanskyCKP14}.  We note that the secure sketch of~\cite{BitanskyCKP14} provides computational unpredictability of $W |p$.  Our negative result that implies that $W|p$ cannot have pseudoentropy~(discussion in \secref{sec:feas comp sec sketch}).

Second, we can weaken the computational assumption necessary for $\Hfuzz(W)$ to be sufficient by moving to an interactive setting.
Consider a user, Alice, using a noisy secret to authenticate with a remote server, Bob.  In this setting, Alice could initially send the value $w$ to Bob and then authenticate with subsequent value $w'$.  If the server holds $w$ and the user $w'$ the two parties can agree on a key using an interactive protocol.
%\footnote{It is dangerous to allow a remote server access to original reading $w$ as they can then impersonate the user.  Ideally, the server would keep a ``hashed'' value of $w$.  This is  done for noiseless secrets like passwords.}  
In this world, secure two-party computation can produce a key whenever the distribution $W$ has fuzzy min-entropy.  The minimal assumption necessary for two party computation is oblivious transfer~\cite{yao1986generate,lindell2009proof}.\lnote{OT, right?; we can ask Ran about their paper with Tal R. or read the paper}

@@

\subsection{Fuzzy Extractors for families of distributions}\label{sec:fuzz extractor}

@@

\subsection{Fuzzy min-entropy: a necessary condition}
\label{sec:minimal conditions}

@@

\subsection{Secure Sketches for Flat distributions}
A distribution is flat if all points in its support have the same probability:
\begin{definition}
A distribution $W$ is \emph{flat} if for all $w_0, w_1 \in W$, $\Pr[W=w_0] = \Pr[W=w_1]$.  
\end{definition}

@@

\subsection{Secure sketches for all distributions with $\Hfuzz(W)$}
The worst-case hashing approach does not work for arbitrary sources.  The reason is that some balls may have  many points but low total weight.  Let $W$ be a distribution, denote by $B^1_t$ a ball with $2^{\Hoo(W)}$ points with probability $\Pr[W\in B^1_t] =2^{-\Hoo(W)}$.  Let $B^2_t,..., B^{2^{-\Hoo(W)}}_t$ be balls with one point each with probability $\Pr[W\in B^i_t] = 2^{-\Hoo(W)}$.  Then the hashing algorithm needs to write down $\Hoo(W)$ bits to achieve correctness.  However, with probability $1-2^{-\Hoo(W)}$ the initial reading is outside of $B^1_t$ and the hash completely reveals the point.

@@

\noindent
In our positive results we considered an arbitrary finite metric space.  The relevant parameters were the size of balls and the size of the metric space.  Our negative results are specific to the Hamming metric.
\section{Impossibility of secure sketches for all families with $\Hfuzz$}
\label{sec:family of dist}

@@

\begin{itemize}
\item \propref{prop:each element good}: for all $W\in \mathcal{W}$, $\Hfuzz(W) = \omega (\log n)$. That is, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
\item \propref{prop:distribution uniform}: the distribution $V$ is uniform.
\item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.  Here we show the minimum distance of $V|\sketch(V)$ is at least $t$.
\item \lemref{lem:side info determines sketch}:  for most lines $Z$, the intersection of the support of $V|Z$ and $V | \sketch(V)$ is small.  \\That is, $\tilde{H}_0(V | \sketch(V), Z) < 2$.
\end{itemize}
\end{proof}
\noindent
\textbf{Note:} There is tradeoff between the size of $\mathbb{F}$ and the error tolerance required for the counter example.  By increasing $t$ it is possible to show a counter example for a smaller $\mathbb{F}$.
\subsection{Implications for Computational secure sketches}
\label{sec:feas comp sec sketch}
Fuller et al. showed that computational secure sketches that provide pseudoentropy imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.  %This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.  
The definition of Fuller et al. uses a weak version of pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.

@@

\section{Impossibility of fuzzy extractors for all families with $\Hfuzz$}
\label{sec:imposs fuzz ext}
In the previous section, we showed a family of distributions that does not admit a secure sketch.  We provide a similar result for fuzzy extractors.

>>>>

\paragraph{Fuzzy Min-Entropy}
We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$, thus subverting the security of $\key$ by running $\rep$. Suppose $w$ is sampled from a distribution $W$.   To have the maximum chance that $w'$ is within distance $t$ of $w$, the adversary would want to maximize the total probability mass of $W$ within the ball $B_t(w')$ of radius $t$ around $w'$.
We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_{w'} \Pr[W\in B_t(w')]$.  Observe that this quantity can be bounded in terms of min-entropy: $\Hoo(W) \ge \Hfuzz(W) \ge \Hoo(W)-\log |B_t|$.

@@

In the fuzzy extractor case, the nonsecret value $p$ partitions the metric space into regions that produce a consistent value under $\rep$ (preimages of each $\key$ under $\rep(\cdot, p)$).  For each of these regions, the adversary knows that possible $w$ lie $t$-far from the boundary of the region.  However, in the Hamming space, the vast majority of points lie near the boundary (this follows by combining the isoperimetric inequality~\cite{harper1966optimal} showing that the ball has the smallest boundary and Hoeffding's inequality~\cite{hoeffding1963probability} for bounding the volume that is $t$-away from this boundary).  This allows the adversary to rule out so many possible $w$ that, combined with the adversarial knowledge of the affine line, many regions become empty, leaving $\key$ far from uniform.

The result for fuzzy extractors is delicate.  It uses the fact that $p$ partitions the space into nonoverlapping regions, which is implied by perfect correctness.  Extending this result to imperfect correctness seems challenging and is an interesting open problem. It also uses the fact that there are few points far from the boundary of every region, which is implied by the geometry of  the high-dimensional Hamming space.  This fact seems crucial: in contrast, in low-dimensional Euclidean space, which does not have this property, a single fuzzy extractor can work for any distribution with sufficient $\Hfuzz$. (Such a construction would use quantization or tiling, similar to, for example, \cite{CK03,LT03,CZC04,LC06,BDHTV10,VTOSS10}.  Each sample from $W$ would map to the ``tile'' containing it, from which the output key would be extracted. A randomly chosen quantizer would have the property that few samples lie near the boundary, giving almost-perfect correctness; if perfect correctness is desired, we can give up on security for those rare samples and simply use a special value of $p$ to indicate that one of them was the input.)

\subsection{Sufficiency of $\Hfuzz$ in Related Settings}
\label{sec:related settings}
The security definition of fuzzy extractors and secure sketches can be weakened to protect only against computationally bounded adversaries~\cite{fuller2013computational}.   In this computational setting, fuzzy extractors and secure sketches can be constructed for the family of all distributions $W$ with superlogarithmic $\Hfuzz$ by using virtual grey-box obfuscation for all circuits~\cite{BitanskyCKP14}. The construction places into $p$ the obfuscated program for testing proximity to $w$ and outputting the appropriate value if the test passes.  In addition to relying on strong assumptions for security (namely, the existence of semantically-secure multilinear maps), this construction is not of practical efficiency. Note that if this construction is used for a secure sketch, $W$ will remain unpredictable conditioned on $p$, but will not have pseudoentropy (see  \secref{sec:feas comp sec sketch} for details).

Furthermore, the functional definition of fuzzy extractors and secure sketches can be weakened to permit interaction between the party having $w$ and the party having $w'$. Such a weakening is useful for secure remote authentication~\cite{Boyen05secureremote}. When both interaction and computational assumptions are allowed, secure two-party computation can produce a key that will be secure whenever the distribution $W$ has fuzzy min-entropy.  The two-party computation protocol needs to be secure without assuming authenticated channels; it can be built under the assumptions that collision-resistant hash functions and enhanced trapdoor permutations exist~\cite{DBLP:journals/joc/BarakCLPR11}.

@@

\subsection{Fuzzy Extractors for Families of Distributions}\label{sec:fuzz extractor}

@@

\subsection{Fuzzy min-entropy: a Necessary Condition}
\label{sec:minimal conditions}

@@

\subsection{Flat distributions}
A distribution is flat if all points in its support have the same probability:
\begin{definition}
A distribution $W$ is \emph{flat} if for all $w_0, w_1 \in W$, $\Pr[W=w_0] = \Pr[W=w_1]$.  
\end{definition}

@@

\subsection{Arbitrary Distributions}
The worst-case hashing approach does not work for arbitrary sources.  The reason is that some balls may have  many points but low total weight.  Let $W$ be a distribution, denote by $B^1_t$ a ball with $2^{\Hoo(W)}$ points with probability $\Pr[W\in B^1_t] =2^{-\Hoo(W)}$.  Let $B^2_t,..., B^{2^{-\Hoo(W)}}_t$ be balls with one point each with probability $\Pr[W\in B^i_t] = 2^{-\Hoo(W)}$.  Then the hashing algorithm needs to write down $\Hoo(W)$ bits to achieve correctness.  However, with probability $1-2^{-\Hoo(W)}$ the initial reading is outside of $B^1_t$ and the hash completely reveals the point.

@@

\noindent
In our positive results we considered an arbitrary finite metric space.  The relevant parameters were the size of balls and the size of the metric space.  Our negative results are specific to the Hamming metric.
\section{Impossibility of Secure Sketches for all Families with $\Hfuzz$}
\label{sec:family of dist}

@@

\begin{itemize}
\item \propref{prop:each element good}: for all $W\in \mathcal{W}$, $\Hfuzz(W) = \omega (\log n)$. That is, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
\item \propref{prop:distribution uniform}: the distribution $V$ is uniform.
\item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.  Here we show the minimum distance of $V|\sketch(V)$ is at least $t$.
\item \lemref{lem:side info determines sketch}:  for most lines $Z$, the intersection of the support of $V|Z$ and $V | \sketch(V)$ is small.  \\That is, $\tilde{H}_0(V | \sketch(V), Z) < 2$.
\end{itemize}
\end{proof}
\noindent
\textbf{Note:} There is tradeoff between the size of $\mathbb{F}$ and the error tolerance required for the counter example.  By increasing $t$ it is possible to show a counter example for a smaller $\mathbb{F}$.
\subsection{Implications for Computational Secure Sketches}
\label{sec:feas comp sec sketch}
Fuller et al. showed that computational secure sketches that provide pseudoentropy imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.  %This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.  
The definition of Fuller et al. uses a weak version of pseudoentropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.

@@

\section{Impossibility of Fuzzy Extractors for all Families with $\Hfuzz$}
\label{sec:imposs fuzz ext}
In the previous section, we showed a family of distributions that does not admit a secure sketch.  We provide a similar result for fuzzy extractors.
